Data_Setup

### 2020-07-22 data-raw/Data_Setup.Rmd
Add new trait documentation for Li for QTL mapping

# Make phenotypes for flowering time paper from all the cleaned phenotypes.

@@

cGDD between GR50 and FL50 for each YEAR, each PLANT_ID (and PLOT_GL)
```{r}
wea_df <- ptt_df %>%
  dplyr::select(DOY:GDD_12C_SM, PTT_12C)

@@

wea_gr_fl3 <- wea_gr_fl %>%
  group_by(Day_of_year, PLOT_GL, PLANT_ID) %>%
  filter(between(Day_of_year, FL50-5, FL50)) %>% 
  ungroup() 
crain_df <- wea_gr_fl3 %>%
  group_by(SITE, PLANT_ID, PLOT_GL, GR50, FL50) %>%
  summarise(CGDD_12C_5d = sum(GDD_12C_SM),
            PTT_12C_5d = sum(PTT_12C),
            CRAIN_5d = sum(RAIN_SM)
            )

cumweadf <- cgdd_df %>%
  left_join(crain_df)

write_rds(cumweadf, path = "../data/Julian_date_GDD_and_rainfall_phenotypes_4wcr_and_gwas.rds")

```
# All phenotypes
```{r}
phe_all <- read_rds("../data/Julian_date_GDD_and_rainfall_phenotypes_4wcr_and_gwas.rds")
phenology <- read_rds("../data/Phenology_phenotypes_4wcr_and_gwas.rds")
```

>>>>

### ------
# Make phenotypes for flowering time paper from all the cleaned phenotypes.

@@

cGDD between GR50 and FL50 for each YEAR, each PLANT_ID (and PLOT_GL)
```{r}
wea_df <- ptt_df %>%
  dplyr::select(DOY:GDD_12C_SM, PTT_12C) %>%
  group_by(SITE) %>%
  mutate(dyln_change_sec = (DYLN - lag(DYLN))*60*60)

@@

wea_gr_fl3 <- wea_gr_fl %>%
  group_by(Day_of_year, PLOT_GL, PLANT_ID) %>%
  filter(between(Day_of_year, FL50-5, FL50)) %>% 
  ungroup() 
crain_df <- wea_gr_fl3 %>%
  group_by(SITE, PLANT_ID, PLOT_GL, GR50, FL50) %>%
  summarise(CGDD_12C_5d = sum(GDD_12C_SM),
            PTT_12C_5d = sum(PTT_12C),
            CRAIN_5d = sum(RAIN_SM)
            )
wea_gr_fl4 <- wea_gr_fl %>%
  ungroup() %>%
  group_by(Day_of_year, PLOT_GL, PLANT_ID) %>%
  filter(Day_of_year == FL50) %>% 
  rename(dyln_fl50 = DYLN) %>%
  dplyr::select(-(TMAX:Day_of_year), -(TMAX_SM:PTT_12C))

cumweadf <- cgdd_df %>%
  left_join(crain_df) %>%
  left_join(wea_gr_fl4)

write_rds(cumweadf, path = "../data/Julian_date_GDD_and_rainfall_phenotypes_4wcr_and_gwas.rds")
```
### -------

# All phenotypes
```{r}
phe_all <- read_rds("../data/Julian_date_GDD_and_rainfall_phenotypes_4wcr_and_gwas.rds")
phenology <- read_rds("../data/Phenology_phenotypes_4wcr_and_gwas.rds")
```
